Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?

### 2016-09-27 ms/ms.tex
ms.tex

@@

Reaching the optimal measurement of the centroids of stars however, is limited
by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
both sky noise and CCD readout noise. Thus we want to investigate whether fast centroiding 
estimates can saturate the bound in a realistic range of signal-to-noise ratios.

@@

We note that the conditions of stationary noise process and uncorrelated Gaussian noise,  may not be representive of many realistic scenarios. 
For instance, in a situation where there is substantial contribution from instruement gain---more effective for the 
bright sources---to the noise, the last two conditions are not met. In this study however, we are only going to consider relatively faint stars, 
for which the assumption of a Gaussian background noise is valid.

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}

@@

Saturating the Cram\'{e}r-Rao lower bound in estimating the centroids of stars however, is limited
by the lack of knowledge about the exact shape of the PSF, also presence of noise. 
There are many sources of noise such as the CCD readout noise, sky noise, errors resulting from 
\todo{incorrect} flatfield corrections, and photon noise from the astronomical object itself. 
In this study, we limit our investigation to the simulated images that contain non-overlapping faint sources 
that are sky-limitted. We assume that the generated images are not affected by flatfield corrections.

However, we focus the scope of this investigation to sky-limited images for which the sky level has been 
subtracted. Furthermore, we assume that any instruement gain has been calibrated out, and that the 
simulated images are free of any contamination by cosmic rays, stray light from neighboring fields, or 
any other type of defect in real images. We expect these defects to move the centroiding errors further from the 
fundamental bound.

We intend to investigate whether fast centroiding 
estimates can saturate the bound in a realistic range of low signal-to-noise ratio images that are sky-limited.

@@

\todo{HOGG HELP: can you read the following paragraph and see whether it makes sense or not?}

Note that in this study, we explicitly focus on sky-limited images. In the sky-limited images, the contribution 
to the Poisson pixel noise is largely domiated by the sky rather than the objects. The exceptions are the very bright 
sources, but we only consider relatively low signal-to-noise ratio faint stellar sources. After subtraction of the 
sky background level, distribution of the Poisson pixel noise can be approximated by a Gaussian distribution with 
zero mean. \todo{Also mention in the discussion: The assumption of uncorrelated Gaussian noise is only an approximation 
to a Poisson distribution which has broader tails than what we expect from a Gaussian!} 
\todo{HOGG HELP: can you write a few words about uncorrelated noise?}

@@

\todo{Given that the authors are using simulated data, a direct search for biases in the estimator outputs is far more powerful than using violations of the Cramer-Rao inequality to infer biased techniques.}

@@

\todo{HOGG HELP: can you read the following paragraph and maybe add a few words to it?}

Note that in our PSF simulations, we assume that the individual generated images are 
Nyquist sampled. All pixels in the images are identical, and the stars are simulated 
by sampling from the pixel-convolved PSF. In well-sampled images, the center of 
the pixel-convolved PSF must be very close to the center of the optical PSF.

@@

\todo{The use of a 7x7 kernel appears arbitrary. For the sake of a fair comparison with the matched filter, the size of the kernel should be equivalent to that used in the matched filter section.}

@@

\todo{ The authors imply the PSF-fitting can only be used when the PSF is known. This is not true; one of the variables in PSF-fitting algorithms is often the PSF size (and sometimes shape) itself.}

@@

\todo{The authors should quantify the difference in accuracy between the 7x7 moment method and an optimal estimator. Is it 10$\%$ worse? 10 times worse?}

@@

\todo{The intent of the statement that the default polynomial centroiding uses only a 3x3 pixel region of the smoothed image is unclear. While this is a factually true statement, the smoothing algorithm requires far more than 3x3 pixels on the original image to operate.}

@@

\todo{If PSF-fitting is to be argued against for speed reasons, the authors should compare the speed of PSF-fitting astrometry and flux estimates against matched filter astrometry plus PSF-fitting flux estimation. It is not clear that the PSF-fitting only approach would be slower, given that the matched filter requires a convolution as well as something with the accuracy of PSF-fitting to estimate flux.}

@@

\todo{It should be noted that estimation of a PSF within a few tenths of a pixel is trivial from most images. Thus, when dealing with realistic images, there is little if any difference between a true matched filter and the default polynomial.}
